### 2016-05-31 R/ITHIM.Rmd
Updated ITHIM.Rmd

```{r AF, echo = FALSE}
with(comparitiveRisk, as.data.frame(lapply(AF[c("BreastCancer","Depression")], function(x) 100*round(x[-(1:2),],4))))
```
### Relative Risk Model
```{r explore}
names(ITHIM.baseline$parameters)
```
```{r RRFigure, echo = FALSE}
phi <- function(x,k=0.5,phi0=comparitiveRisk$RR.baseline$BreastCancer$F[1,1]) phi0^{x^k}
plot(x = xvec <- seq(0,xmax <- 10,length.out=1e3), y = phi(xvec, k = 0.25), main = "Relative Risk Models for MET Exposure", xlab = "METs per week", ylab = "Breast Cancer Relative Risk", type = "l", lwd = 2, col = 1, ylim = c(0.9,1),xlim=c(0,xmax))
lines(x = xvec <- seq(0,xmax,length.out=1e3), y = phi(x = xvec, k = 0.375), lwd = 2, col = 3)
lines(x = xvec <- seq(0,xmax,length.out=1e3), y = phi(x = xvec, k = 0.5), lwd = 2, col = 2)
lines(x = xvec <- seq(0,xmax,length.out=1e3), y = phi(x = xvec, k = 1), lwd = 2, col = 4)
legend(x="topright",legend=paste0("k=",c("0.25","0.375","0.5","1")), col=1:4,lty=1,lwd=2)
```

>>>>

```{r AF, echo = FALSE}
with(comparitiveRisk, as.data.frame(lapply(AF[c("BreastCancer","Depression")], function(x) 100*round(x[-(1:2),],4))))
```
```{r ap}
k <- createAirPollutionRRs()
```

### Relative Risk Model
```{r explore}
names(ITHIM.baseline$parameters)
```
```{r RRFigure, echo = FALSE}
phi <- function(x,k=0.5,phi0=comparitiveRisk$RR.baseline$BreastCancer$F[1,1]) phi0^{x^k}
plot(x = xvec <- seq(0,xmax <- 10,length.out=1e3), y = phi(xvec, k = 0.25), main = "Relative Risk Models for MET Exposure", xlab = "METs per week", ylab = "Breast Cancer Relative Risk", type = "l", lwd = 2, col = 1, ylim = c(0.9,1),xlim=c(0,xmax))
lines(x = xvec <- seq(0,xmax,length.out=1e3), y = phi(x = xvec, k = 0.375), lwd = 2, col = 3)
lines(x = xvec <- seq(0,xmax,length.out=1e3), y = phi(x = xvec, k = 0.5), lwd = 2, col = 2)
lines(x = xvec <- seq(0,xmax,length.out=1e3), y = phi(x = xvec, k = 1), lwd = 2, col = 4)
legend(x="topright",legend=paste0("k=",c("0.25","0.375","0.5","1")), col=1:4,lty=1,lwd=2)
```
